% resume, made using the moderncv template
% https://github.com/xdanaux/moderncv

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{lastpage}
\usepackage[scale=0.75]{geometry}
\usepackage{ulem}



% theme

\moderncvstyle{classic}
\moderncvcolor{blue}

\newfontfamily\yanone[]{YanoneKaffeesatz-Regular}
\setsansfont{Liberation Sans}
\rfoot{\addressfont\itshape\textcolor{color2}{\thepage{} / \pageref{LastPage}}}
\renewcommand{\ULdepth}{1.8pt}

\renewcommand{\homepagesymbol}{\faHome~}
\renewcommand*{\namefont}{\yanone\fontsize{42}{42}\mdseries\upshape}
\renewcommand*{\titlefont}{\yanone\fontsize{22}{22}\mdseries\upshape}
\newcommand{\myhref}[2]{\href{#1}{\color{color1!64!color2}\uline{#2}}}%
\setlength{\leftmargini}{2em}



% personal info

\name{Antoine}{Leblanc}
\title{Software engineer, Haskell teacher,\newline{}video games developer, demoscener}
\email{antoine.jp.leblanc@gmail.com}
\homepage{www.nauths.fr/en}
\social[linkedin]{antoineleblanc}
\social[twitter]{nicuveo}
\social[github]{nicuveo}



% document

\begin{document}

\makecvtitle

\vspace{0.4cm}

\section{Experience}
\cventry[1em]{2020-2023}{Senior Software Engineer / Team Lead / Tech Lead}{Hasura}{Remote}{}{%
Major contributor to the 2.0 rewrite, including:%
\begin{itemize}%
\item \myhref{https://github.com/hasura/graphql-engine/pull/4111}{full rewrite}  of the core of the engine.
\item generalization of the engine to \myhref{https://hasura.io/blog/building-a-graphql-to-sql-compiler-on-postgres-ms-sql-and-mysql/}{multiple backends}
\end{itemize}
Main contributor to the \myhref{https://hasura.io/docs/latest/remote-schemas/remote-relationships/index/}{generalized remote relationships} feature.\newline{}
Lead the data-sources team throughout the MSSQL and Citus integrations.\newline{}
Lead an internal effort to improve / consolidate engineering documentation.\newline{}
Lead an internal effort to modularize / untangle the codebase.\newline{}
Onboarding and mentoring of server engineers.\newline{}
Wrote \myhref{https://hasura.io/blog/parser-combinators-walkthrough/}{an article} to help with Haskell outreach.%
}
\cventry[1em]{2020}{Mentor}{exercism}{}{}{%
  Weekly volunteering effort: mentor on the Haskell track.%
}
\cventry[1em]{2019}{Software Engineer}{Stripe}{Dublin}{}{%
  Worked on SAML authentication flows for Stripe's dashboard.\newline{}
  Rewrote all login flows, both frontend (React) and backend (Ruby).\newline{}
  On-call and customer support rotation.%
}
\cventry[1em]{2015 -- 2019}{Site Reliability Engineer}{Google}{Dublin}{}{SRE for Bigtable and Cloud Bigtable:%
\begin{itemize}%
\item Defined \myhref{https://cloud.google.com/bigtable/}{Cloud Bigtable}'s orginal \myhref{https://en.wikipedia.org/wiki/Service-level_objective}{SLOs} and \myhref{https://en.wikipedia.org/wiki/Service-level_agreement}{SLAs}.
\item Integrated an experiment framework in Cloud Bigtable's codebase.
\item Rewrote the resource planning pipeline to better predict users' demand.
\item On-call for the service.
\end{itemize}\vspace{0.4em}%
Haskell teacher (20\% time):%
\begin{itemize}%
\item Created two lessons (101, 102) and relevant exercises.
\item Taught them worldwide, reaching more than 600 people, 95\% approval rate.
\end{itemize}\vspace{0.4em}%
Community contributions:%
\begin{itemize}%
\item Presented SRE at Google Cloud Summit (on \myhref{https://youtu.be/ZKbU5OIXuxs}{YouTube}, in French).
\item Worked with VP of Diversity to improve Google's response to online threats.
\item Started an effort to make all Google code and documentation gender neutral.
\item Started an initiative to teach computer science basics to non-engineers.
\end{itemize}}
\cventry[1em]{2012 -- 2015}{Software Engineer}{Criteo}{Paris}{}{%
  Worked on / maintained Criteo's ad arbitrage and ad serving pipeline.\newline{}
  Developed a small ad-hoc continuous testing platform.}
\cventry[1em]{2009 -- 2012}{Cofounder}{Altribe}{Paris}{}{%
  Created a startup focused on massively multiplayer online strategic games.\newline{}%
  Developed the game client for our first project:%
\begin{itemize}%
\item Multi-platform codebase, using C++, Boost, Qt, and OpenGL.
\item Developed a tiled map renderer from scratch, using
  render-to-texture and interpolation between different zoom levels.
\end{itemize}}

\vspace{0.6em}
\section{Awards}
\cventry{2015}{Best Dev of France}{}{}{}{First place in the \textit{Meilleur Dev de France} contest, since then renamed to \myhref{https://www.masterdevfrance.com}{Master Dev France}.}
\cventry{2018}{Arms Control Person of the Year}{}{}{}{Alongside \myhref{https://www.armscontrol.org/pressroom/2018-acpoy-winner}{4000 other Googlers}.}

\vspace{0.6em}
\section{Education}
\cventry{2004 -- 2009}{CS engineering degree}{\myhref{http://international.epita.fr}{EPITA}}{Paris}{}{Student / researcher at the \myhref{http://international.epita.fr/research-development-laboratory.aspx}{LRDE}, EPITA's R\&D lab.\newline{}Graduated from the Research major.}
\cventry{2009}{Software Engineering Intern}{Dassault Systèmes}{Vélizy (France)}{}{Six months internship (February -- July).\newline{}Performance analysis of a surface deformation and animation algorithm.}

\vspace{0.6em}
\section{Projects, hobbies}
\cvitem{Demoscene}{Former member of the \myhref{http://www.ctrl-alt-test.fr}{Ctrl-Alt-Test} demoscene group.\newline{}\myhref{http://www.ctrl-alt-test.fr/productions/b-incubation/}{B - incubation}:%
\begin{itemize}%
\item 1st place at \myhref{https://www.evoke.eu}{Evoke} 2010;
\item nominated for 2010 Scene Awards for breakthrough performance.
\vspace{-\baselineskip}\mbox{}
\end{itemize}}
\cvitem{Live coding}{Solving and explaining problems, usually in Haskell, on \myhref{https://www.twitch.tv/nicuveo}{Twitch}.}
\cvitem{Volunteering}{Former member of the charity choir \myhref{http://note-et-bien.org}{Note et Bien}.}

\vspace{0.6em}
\section{Languages}
\cvitem{English}{Fluent}{}
\cvitem{French}{Native speaker}{}
\cvitem{Japanese}{\myhref{https://www.jlpt.jp/e/about/levelsummary.html}{N5 level}}{}
\cvitem{German}{High-school level}{}

\clearpage
\section{Obligatory skills list}
\cvitem{Languages}{C++, Haskell, Python, Rust, Ruby, Bash\ldots{}}{}
\cvitem{Presentation}{\LaTeX{}, Beamer}{}
\cvitem{Editor}{Emacs}{}

\vspace{0.6em}
\section{Misc}
\cvitem{CV}{This CV was made with \LaTeX. Sources can be found on \myhref{https://github.com/nicuveo/CV}{Github}.}

\end{document}
